\section{Related work}
\label{sec:related_work}

Existing research suggests six different solutions for
  the problem of identity on the SW.

\textbf{[1] Introduce weaker versions of {\small \texttt{owl:sameAs}}}
  \cite{HalpinHayes2010,MccuskerMcguinness2010}.
Candidates for replacement are
  the SKOS concepts
  {\small \texttt{skos:related}} and {\small \texttt{skos:exactMatch}}
  \cite{MilesBechhofer2009}.
The former is not transitive,
  thereby limiting the possibilities for reasoning.
The latter is transitive,
  but can only be used in certain contexts.
It is not defined in what contexts it can be used
  \cite{MilesBechhofer2009}.

\textbf{[2] Restrict the applicability of identity relations}
  to specific contexts.
In terms of SW technology, identities are expected to hold
  within a named graph or within a namespace,
  but not necessarily outside of it \cite{HalpinHayes2010}.
\cite{Melo2013} has successfully used the Unique Names Assumption
  within namespaces in order to identify many (arguably) spurious
  identity statements.

\textbf{[3] Introduce additional vocabulary} that does not weaken but extend
  the existing identity relation.
\cite{HalpinHayes2010} mention an explicit distinction that can be made
  between mentioning a term and using a term.
Other possible extensions of {\small \texttt{owl:sameAs}} take
  the Fuzzyness and/or uncertainty of identity statements into account.

\textbf{[4] Use domain-specific identity relations}
  \cite{MccuskerMcguinness2010}.
For instance
    ``$x$ and $y$ have the same medical use''
  replaces
    identity in the domain of medicine,
and
    ``$x$ and $y$ are the same molecule''
  replaces
    identity in the domain of chemistry.
Such domain-specific links are only locally valid,
  thereby limiting knowledge reuse.

\textbf{[5] Change the modeling practice}, possibly in a (semi-)automated way
  by adapting visualization and modeling toolkits to produce notifications
  upon reading SW data, or by posing additional restrictions on the creation
  and alteration of data
  \cite{HalpinHayes2010,DingShinavierFininMcguinness2010}.
Introducing checks on editing operations violates
  one of the fundamental underpinnings of the SW:
  that anybody is allowed to say anything about anything
  \cite{AntoniouGrothHarmelenHoekstra2012}.

We also mention \cite{DingShinavierShangguanMcguinness2010} who show that
  network analysis of the occurrence of {\small \texttt{owl:sameAs}}
  in datasets can provide insights into the ways in which identity is used.
These latter endeavors have not yet been related to the semantics of
  identity.

%What the existing approaches have in common is
%  that quite some work has to be done --
%  adapting or creating standards, instructing modelers, converting existing
%  datasets -- in order to resolve only some of the problems of identity.
%Our approach provides a way of dealing with the heterogeneous real-world
%  usage of identity in the SW that is fully automated and requires
%  no changes to standards, modeling practices, or existing datasets.

